New Evidence on the Chinese Environmental Policy Effectiveness in Private versus SOEs\thanks{We would like to thank the editor and anonymous reviewers for their helpful comments.}

### 2020-05-09 Paper/no_author_bis.tex
Second version

\title{New Evidence on the Chinese Environmental Policy Effectiveness in Private versus SOEs\thanks{We would like to thank the editor, anonymous reviewers for their helpful comments. We are also very greatful to Zhao Ruili and Zhou Ling for their precious help in collecting the data from the China Environment Statistics Yearbook.}}
\author{
Mathilde Maurel\thanks{CNRS, France and Centre d'Economie de la Sorbonne, Université Paris 1 Panthéon-Sorbonne, France} 
\and Thomas Pernet\thanks{Centre d'Economie de la Sorbonne, Université Paris 1 Panthéon-Sorbonne, France,
\href{mailto:t.pernetcoudrier@gmail.com}{email: t.pernetcoudrier@gmail.com} 
%email: \href{t.pernetcoudrier@gmail.com}
}
}

@@

The findings are robust to the inclusion of different specifications of fixed effects, and other key determinants of firm pollution. Moreover, we investigate what are the main factors behind the no-compliance of SOEs to the regulations: the location (or not) in TCZ (SPZ, Coastal) cities where the environmental (growth) policies are prioritized, the existence of turning points below (above) which growth and decrease in pollution substitute (complement) each other, the size and degree of industrial concentration which determine the possibility for firms to negotiate with the local authorities, and finally the regulation-induced adoption of cleaner technologies among polluting firms, which enhance productivity and decrease the emission of SO2.  \\
\vspace{0em}\\
\noindent\textbf{Keywords:} Environmental regulation, China, Kornai, Soft Budget Constraint, Difference-in-Difference estimation\\
\vspace{0em}\\
\noindent\textbf{JEL Codes:} Q53,Q56,P2,R11
\\

\bigskip
\end{abstract}
\setcounter{page}{0}
\thispagestyle{empty}
\end{titlepage}
\pagebreak \newpage

@@

\begin{table}[!htb] \centering
\caption{\\ SO2 reduction (\%) during the subsequent FYPs}
\label{table_1}
\begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
\begin{tabular}{lrrrr}
\toprule
             Cities &  1998-2001 &  2002-2005 &  2006-2010 &  Target \\
\midrule
             No TCZ &     21 &     64 &    -11 &  -6 \\
                TCZ &     -7 &     38 &    -15 & -16 \\
 $\text{No Dominated SOE}^ a$ &    -31 &     30 &    -16 & -10 \\
 $\text{Dominated SOE}^ a$ &      6 &     21 &    -17 & -12 \\
        Full Sample &     -2 &     45 &    -13 & -10 \\

\bottomrule
\end{tabular}
\end{adjustbox}
\begin{tablenotes} 
 \small 
 \item 
Sources: Author's own computation \\
The list of TCZ is provided by the State Council, 1998.
"Official Reply to the State Council Concerning Acid Rain Control Areas
and Sulfur Dioxide Pollution Control Areas".
The information about the SO2 level are collected using various editions
of the China Environment Statistics Yearbook.
We compute the reduction of SO2 emission using the same methodology
as Chen and al.(2018). \\
$a$ (No) Dominated SOEs cities refer to cities where the 
(output, capital, employment) share of SOEs is (below) above a critical threshold, for instance the 60th decile

>>>>

\title{New Evidence on the Chinese Environmental Policy Effectiveness in Private versus SOEs\thanks{We would like to thank the editor and anonymous reviewers for their helpful comments.}}
\author{}

@@

The findings are robust to the inclusion of different specifications of fixed effects, and other key determinants of firm pollution. Moreover, we investigate what are the main factors behind the no-compliance of SOEs to the regulations: the location (or not) in TCZ (SPZ, Coastal) cities where the environmental (growth) policies are prioritized, the existence of turning points below (above) which growth and decrease in pollution substitute (complement) each other, the size and degree of industrial concentration which determine the possibility for firms to negotiate with the local authorities, and finally the regulation-induced adoption of cleaner technologies among polluting firms, which enhance productivity and decrease the emission of SO2.  \\
\vspace{0em}\\
\noindent\textbf{Keywords:} Environmental regulation, China, Kornai, Soft Budget Constraint, Difference-in-Difference estimation\\
\vspace{0em}\\
\noindent\textbf{JEL Codes:} Q53,Q56,P2,R11
\\
\bigskip
\end{abstract}
\setcounter{page}{0}
\thispagestyle{empty}
\end{titlepage}
\pagebreak \newpage

@@

\begin{table}[!htb] \centering
\caption{\\ SO2 reduction (\%) during the subsequent FYPs}
\label{table_1}
\begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
\begin{tabular}{lrrrr}
\toprule
             Cities &  1998-2001 &  2002-2005 &  2006-2010 &  Target \\
\midrule
             No TCZ &     21 &     64 &    -11 &  -6 \\
                TCZ &     -7 &     38 &    -15 & -16 \\
 $\text{No Dominated SOE}^ a$ &    -31 &     30 &    -16 & -10 \\
 $\text{Dominated SOE}^ a$ &      6 &     21 &    -17 & -12 \\
        Full Sample &     -2 &     45 &    -13 & -10 \\
\bottomrule
\end{tabular}
\end{adjustbox}
\begin{tablenotes} 
 \small 
 \item 
Sources: Author's own computation \\
The list of TCZ is provided by the State Council, 1998.
"Official Reply to the State Council Concerning Acid Rain Control Areas
and Sulfur Dioxide Pollution Control Areas".
The information about the SO2 level are collected using various editions
of the China Environment Statistics Yearbook.
We compute the reduction of SO2 emission using the same methodology
as Chen and al.(2018). \\
$a$ (No) Dominated SOEs cities refer to cities where the 
(output, capital, employment) share of SOEs is (below) above a critical threshold, for instance the 60th decile
